### 2014-10-28 Draft/abstract.tex
Space after ICON in abstract Removed duplicate assist

\textbf{Results}: To evaluate our approach, we apply \tool to infer temporal
constraints from commonly used package \CodeIn{java.io} in the
JDK API and from the \amazonAPI. Our results show
that \tool\ effectively identifies constraint sentences (from over
3900 API sentences) with the average precision, recall, and F-score
of 65.0\%, 72.2\%, and 68.4\%, respectively. Furthermore, \tool\
also achieves an accuracy of 70\% in inferring 63 temporal constraints
from these sentences.

@@

\textbf{Application}: Existing software engineering tools can leverage
the inferred temporal constraints to effectively assist assist in development
and verification activities.

>>>>

\textbf{Results}: To evaluate our approach, we apply \tool\ to infer temporal
constraints from commonly used package \CodeIn{java.io} in the
JDK API and from the \amazonAPI. Our results show
that \tool\ effectively identifies constraint sentences (from over
3900 API sentences) with the average precision, recall, and F-score
of 65.0\%, 72.2\%, and 68.4\%, respectively. Furthermore, \tool\
also achieves an accuracy of 70\% in inferring 63 temporal constraints
from these sentences.

@@

\textbf{Application}: Existing software engineering tools can leverage
the inferred temporal constraints to effectively assist in development
and verification activities.
